Beta to Release Matching

### 2019-09-11 report_poc.Rmd
Adding report markdown and supporting modeling file.

# single dataframe for plotting
df_f <- exp_4x.nearest.ma.df %>% 
  select(-c(distance, weights)) %>%
  filter(label == 'beta') %>%
  mutate(label =  'beta - matched') %>%
  rbind(df_4x_sm)
```

@@

[Statistical matching](https://en.wikipedia.org/wiki/Matching_(statistics)) methods were employed to investigate the posssibility of finding a subset of Beta clients that are representative of Release. The specific use-case of this proof-of-concept is utilizing engagement, configuration, and environment client fields (covariates) for matching. Validation of the matching is performed on a hold-out set of Firefox performance covariates, as an illustration of a potential real-world use-case. The following tables represent the relative difference between Beta and Release for the mean and median respectively. These initial results are promising and suggest that such techniques can work.

@@

### Covariates
The following covariates are collected. These are categorized under training, and hold-out. The former are used for training a statistical matching model. The latter are not included in training and are used for determining model performance. The covariates are further subcategorized as to the what they measure.

#### Training
The sum of <  > ....
(build markdown table)

#### Holdout
The following are the performance metrics used for validation. The

@@

## Models
A range of statistical matching models were reviewed, using the _R_ library [Matchit](https://cran.r-project.org/web/packages/MatchIt/index.html):

@@

Mahalanobis distance matching requires continuous covariates. The following were found to be the most performant:

< covariates>

@@

However, for `MEMORY_TOTAL` and `startup_ms`, the improvement is marginal and the resultant matched distrubution are poor. `MEMORY_TOTAL` has the greatest observable difference between Beta and Release pre and post matching. `startup_ms` doesn't appear to be highly distinct across channels for these metrics.

Combined, these results suggest that matching can make small, but limited, improvements to the distributions.

@@

model_covs <- c('search_count', 'daily_max_tabs', 'daily_num_sessions_started', 'num_addons', 
                                        'num_bookmarks', 'profile_age', 'timezone_offset', 'cpu_speed_mhz', 'memory_mb', 
                                        'cpu_cores')

@@

The matching did an adequate job in finding a representative subset of Beta, especially concerning the performance metrics task. There are many avenues to further this analsysis, in order to utilize such a methodology in a production setting:

* Covariate/ Variable selection
  * This needs to be actively researched, especially in regards to real-world Firefox use-cases. 
* Compare histogram distributions
  * Client means were utilized in this above analysis. Instead, aggregating the client distributions needs to be addressed.
* Feature generation
  * The covariates utilized above are limited subset. A much more rigorous analysis of covariates needs to be applied.
* All countries used in matching
  * This is required for most general uses of the Beta subset.
  * The US and GB Beta population is quite small. As noted above, overrepresentation of Beta in matching results in higher performant models. Therefore, to obtain greater training sample sizes requires at minimum for India to be considered.

>>>>

# single dataframe for plotting
df_f <- exp_4x.nearest.ma.df %>% 
  select(-c(distance, weights)) %>%
  filter(label == 'beta') %>%
  mutate(label =  'beta - matched') %>%
  rbind(df_4x_sm)

model_covs <- c('search_count', 'daily_max_tabs', 'daily_num_sessions_started', 'num_addons', 
                                        'num_bookmarks', 'profile_age', 'timezone_offset', 'cpu_speed_mhz', 'memory_mb', 
                                        'cpu_cores')
```

@@

[Statistical matching](https://en.wikipedia.org/wiki/Matching_(statistics)) methods were employed to investigate the posssibility of finding a subset of Beta clients that are representative of Release. The specific use-case of this proof-of-concept was to utilize engagement, configuration, and environment client fields (covariates) for matching. Validation of the matching was performed on a hold-out set of Firefox performance covariates, as an illustration of a potential real-world use-case. The following tables represent the relative difference between Beta and Release for the mean and median respectively. These initial results are promising and suggest that such techniques can work.

@@

### Covariates
The following covariates were collected. These were categorized under training, and hold-out. The former were used for training a statistical matching model. The latter are not included in training and are used for determining model performance. The covariates are further subcategorized as to the what they measure.

#### Training

* Browser engagement
    - uri_count
    - search_count
    - active_hours
    - num_pages
    - daily_max_tabs
    - daily_unique_domains
    - daily_num_sessions_started
    - daily_tabs_opened
* Frequency of Browser Usage
    - num_active_days
    - daily_num_sessions_started
    - session_length
    - profile_age
* Environment
    - cpu_cores
    - cpu_speed_mhz
    - memory_mb
    - os
    - os_version
    - is_wow64
    - distribution_id
* Geo
    - country
    - timezone_offset
* Settings
    - num_bookmarks
    - num_addons
    - sync_configured
    - is_default_browser

#### Holdout
The following are the performance metrics used for validation. These were chosen to cover various aspects of [Firefox performance](https://docs.google.com/document/d/1W-EREsJLuRvTPvGXaW71FvuAGXkoLNDZmZl-sbaeMZM/edit#heading=h.xguata2qq3jz), in addition to their ease of accessbility in `main_summary`,

* Page Load
    - FX_PAGE_LOAD_MS_2_PARENT
    - TIME_TO_DOM_COMPLETE_MS
    - TIME_TO_DOM_CONTENT_LOADED_END_MS
    - TIME_TO_LOAD_EVENT_END_MS
* Responsiveness
    - FX_TAB_SWITCH_TOTAL_E10S_MS    
* Graphics
    - COMPOSITE_TIME_GPU
    - CONTENT_FRAME_TIME_GPU
    - CONTENT_PAINT_TIME_CONTENT
* Memory
    - MEMORY_TOTAL
* Startup
    - startup_ms
* Stability
    - content_crashes

@@

## Models
A range of statistical matching models were [reviewed](https://metrics.mozilla.com/protected/cdowhygelund/modeling_poc.Rmd), using the R library [Matchit](https://cran.r-project.org/web/packages/MatchIt/index.html):

@@

Mahalanobis distance matching requires continuous covariates. The following were found to be the most performant: `r paste(model_covs, sep=', ', collapse = ', ')`.

@@

However, for `MEMORY_TOTAL` and `startup_ms`, the improvement is marginal and the resultant matched distrubutions are poor. `MEMORY_TOTAL` has the greatest observable difference between Beta and Release pre and post matching. `startup_ms` doesn't appear to be highly distinct across channels for these metrics.

In all cases, the change in the metrics is always positive. Combined, these results suggest that matching can make significant, albeit limited, improvements to the distributions.

@@

@@

The matching did an adequate job in finding a representative subset of Beta, especially concerning the performance metrics task. There are many avenues to further this analsysis, in order to utilize such a methodology in a production setting. The primary research investment that needs to be made is in feature generation and selection. These are typically the highest influential factos in ML/predictive modeling tasks.

Additional next steps include:

* Covariate/ Variable selection
  * This needs to be actively researched, especially in regards to real-world Firefox use-cases. 
* Compare histogram distributions
  * Client means were utilized in this above analysis. Instead, aggregating the client distributions should be addressed.
* Feature generation
  * The covariates utilized above are limited subset. A much more rigorous analysis of covariates needs to be applied.
* Additional countries used in matching
  * This is required for most general uses of the Beta subset.
  * The US + GB Beta population is quite small. As noted above, overrepresentation of Beta in matching yields higher performant models. Therefore, to obtain greater training sample sizes requires additional countries, especially India, to be considered.
